---
title: "Making a Random Forest Model on the College dataset"
output: 
  html_document: 
    fig_height: 4
    highlight: pygments
    theme: spacelab
---

## Setup

### Load packages

```{r load-packages, message = FALSE}
library(ggplot2)
library(dplyr)
library(statsr)
```

### Load data


```{r load-data}
library(ISLR)
head(College)
df<-College
```




* * *

## Part 1: EDA
```{r}

library(ggplot2)
ggplot(df,aes(Room.Board,Grad.Rate)) + geom_point(aes(color=Private))
```

```{r}
ggplot(df,aes(F.Undergrad)) + geom_histogram(aes(fill=Private),color='black',bins=50)
```

```{r}
ggplot(df,aes(Grad.Rate)) + geom_histogram(aes(fill=Private),color='black',bins=50)
```

Reseting Graduation rate to 100% for colleges with more than 100% college graduation rate

```{r}
subset(df,Grad.Rate > 100)
df['Cazenovia College','Grad.Rate'] <- 100
```

* * *

## Part 2: Splitting the data

```{r}
library(caTools)

set.seed(101) 

sample = sample.split(df$Private, SplitRatio = .70)
train = subset(df, sample == TRUE)
test = subset(df, sample == FALSE)
```

* * *

## Part 3: Modeling a Decision Tree
```{r}
library(rpart)
tree <- rpart(Private ~.,method='class',data = train)
```


Predicting the test data

```{r}
tree.preds <- predict(tree,test)

head(tree.preds)
```
Turning these two columns into one column to match the original Yes/No Label for a Private column.

```{r}
tree.preds <- as.data.frame(tree.preds)
joiner <- function(x){
    if (x>=0.5){
        return('Yes')
    }else{
        return("No")
    }
}
```


```{r}
tree.preds$Private<-sapply(tree.preds$Yes,joiner)
```


```{r}
head(tree.preds)
```


```{r}

table(tree.preds$Private,test$Private)
```

Plotting our tree.
```{r}

library(rpart.plot)
prp(tree)
```

## Making a Random Forest Model

```{r}
library(randomForest)
rf.model <- randomForest(Private ~ . , data = train,importance = TRUE, ntree=400)
```


```{r}
rf.model$confusion
```



```{r}
rf.model$importance
```

Making Predictions
```{r}

p <- predict(rf.model,test)
```

```{r}
table(p,test$Private)
```





